Type-Safe Modular Parsing

### 2017-01-14 paper/sections/Introduction.tex
Small space tweak
Note for reviewers

\item {{\bf A technique for Modular Parsing:}} We present a technique
that allows the development of semantically modular parsers.
The technique relies on the combination of Packrat parsing, multiple inheritance
  and Object Algebras.

@@

\item {{\bf TAPL case study:}} We conduct a case study with 18 interpreters
  from the TAPL book. The case study show the effectiveness of modular
  parsing in terms of reuse. The TAPL case study is available online
  at:
  \url{http://}

>>>>

\item {{\bf A Technique for Modular Parsing:}} We present a technique
that allows the development of semantically modular parsers.
The technique relies on the combination of Packrat parsing, multiple inheritance
  and Object Algebras.

@@

\item {{\bf TAPL case study:}} We conduct a case study with 18 interpreters
  from the TAPL book. The case study show the effectiveness of modular
  parsing in terms of reuse. The TAPL case study is available online
  at:
  \url{http://}\footnote{{\bf Note to Reviewers:} Please find the url in the
  suplementary material for the submission.}
